Chaotic Behavior of the Triple Pendulum \\ \large A Computational Approach

### 2017-05-11 paper.tex
progress!

@@

    \section{Introduction}

>>>>

\graphicspath{{figures/}}

@@

\section{Introduction}
In this paper, we will report on our findings regarding the behavior and
motion of an undamped triple pendulum made of three equal masses attached by
three massless rods of equal length. We used the Lagrangian formulation to
create equations of motion for the three masses, then examined the system using
Python. We used Fourier transformations as a tool to help us determine if the
pendulum's motion was chaotic or periodic. \textbf{Did we examine how changing
the masses affects the motion or are we giving up on that?} Our findings helped
us find some order about a system that initially appeared to be purely chaotic.

\section{Conservation of Energy}
After finding our equations of motion for the three masses, we first wanted to
test that they were correct. Our plots of the masses' angles versus time seemed
reasonable, but we wanted to confirm our suspicions before delving deeper into
the problem. We plotted kinetic, potential and total energy versus time on the
same set of axes and saw that mechanical energy of the system is conserved
(Fig. \ref{fig:energy_cons}).
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{energy_conservation}
	\caption{Kinetic, potential, and total energy over time for $\dot\phi_3(0)=\SI{7}{s^{-1}}$.}
	\label{fig:energy_cons}
\end{figure}

\section{Chaotic or Periodic?}
As we first began to examine the system, we kept all initial angles and angular
velocities save for the lowest hanging mass's at zero. For short time frames
and an initial angular velocity of $\dot\phi_3=\SI{7}{s^{-1}}$, the motion of
the system appears to be chaotic. However, increasing the time window to 1,000
seconds showed something different. In Figure \ref{fig:moderate_time}, we can
see that there appears to be some sort of regularity to the pendulum's motion.
Looking at such a plot is not sufficient to declare periodic victory, so we
needed to use some other tools to help us describe the system's motion.
 \begin{figure}
	\centering
	\includegraphics[width=\textwidth]{moderate_velocity_time_sol}
	\caption{$\phi_1,\phi_2$, and $\phi_3$ over time for $\dot\phi_3(0)=\SI{7}{s^{-1}}$}
	\label{fig:moderate_time}
\end{figure}

\section{Results}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{bifurcation_1}
	\caption{``Bifurcation Diagram" for $2\le\dot\phi_3(0)\le 20$}
	\label{fig:bifurc_1}
\end{figure}
